%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Presentations}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
%\vspace{-0.3cm}
%\begin{small}\textit{* presenting author; \textsuperscript{+} mentored undergraduate}\end{small}

%-------------------------------------------------------------------------------
\cvsubsection{Contributed Presentations}
%-------------------------------------------------------------------------------

\begin{cvpubs}

    \cvpub{\textbf{Gutiérrez-Álvarez, C}, Ríos-Navarro P., Flor-Rodríguez-Rabadán R., Acevedo-Rodríguez F.J., López-Sastre R.J., Evaluation of Visual Semantic Navigation Models in Real Robots. Poster and oral presentation: IROS 2023, Detroit, Michigan.}

    \cvpub{\textbf{Gutiérrez-Alvarez C}, Hernández García S, Nasri N, Cuesta-Infante Alfredo, López-Sastre RJ, Towards Clear Evaluation of Robotic Visual Semantic Navigation, in ICARA 2023, Abu Dhabi, United Arab Emirates.}

    \cvpub{\textbf{Gutiérrez-Álvarez, C}, Flor-Rodríguez-Rabadán R., Acevedo-Rodríguez F.J., López-Sastre R.J., Kanezaki.A, OffNav: Offline Reinforcement Learning for Visual Semantic Navigation. Late breaking results at ICRA 2024, Yokohama, Japan.}

    \cvpub{\textbf{Gutiérrez-Álvarez, C}, Flor-Rodríguez-Rabadán R., Acevedo-Rodríguez F.J., López-Sastre R.J., Kanezaki.A, OffNav: Offline Reinforcement Learning for Visual Semantic Navigation. Poster presentation at Human-aligned Reinforcement Learning for Autonomous Agents and Robots Workshop, ICRA 2024, Yokohama, Japan.}

\end{cvpubs}

\cvsubsection{Seminars and workshops}

\begin{cvpubs}

    \cvpub{\textbf{Summer 2023}. \textit{Basics of Robotic Navigation}. Seminar at Axpe Consulting, Madrid, Spain.}

    \cvpub{\textbf{Summer 2024}. \textit{Reinforcement Learning para la robótica}. Workshop at Msc in Telecommunications Engineering, University of Alcalá, Madrid, Spain.}

\end{cvpubs}

%-------------------------------------------------------------------------------
\cvsubsection{Invited Talks}
%-------------------------------------------------------------------------------

\begin{cvpubs}

    \cvpub {\textbf{Spring 2023}. \textit{Abro Micro: Inteligencia artificial e interpretación de conferencias}. Podcast. Madrid, Spain.}

\end{cvpubs}