%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Professional Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
    \cventry
    {Senior Reinforcement Learning Specialist} % Advisor
    {Indra} % Institution
    {Madrid, Spain} % Location
    {May 2025 - Present} % Date(s)
    {
        \begin{cvitems} % Description(s)
            \item {Responsible for the development of reinforcement learning solutions for all critical systems within Indra.}
            \item {Implementation of Gymnasion wrappers for the integration of reinforcement learning algorithms in Indra's several systems.}
            \item {Communication between envs and algorithms using gRPC protocol.}
            \item {Implementation of multi-agent and hierarchical reinforcement learning solutions for complex environments.}
        \end{cvitems}
    }

%---------------------------------------------------------
    \cventry
    {Spanish Science Ministry Pre-doctoral Scholarship} % Advisor
    {University of Alcalá} % Institution
    {Alcalá de Henares, Spain} % Location
    {Sep. 2021 - May 2025} % Date(s)
    {
        \begin{cvitems} % Description(s)
            \item {Doctoral Thesis: ``Reinforcement Learning for Visual Semantic Navigation”}
            \item {Working with a FPI scholarship by Spanish Science Ministry.}
        \end{cvitems}
    }

%---------------------------------------------------------
    \cventry
    {Co-Founder} % Advisor
    {TourQuiz} % Institution
    {Alcalá de Henares, Spain} % Location
    {Dic. 2021 - Mar. 2022} % Date(s)
    {
        \begin{cvitems} % Description(s)
            \item {Development of TourQuiz App: A mobile app for gamified turistic tours.}
            \item {The app uses flutter and firebase technologies to bring a new experience to turistic tours.}
            \item {It proposes a 360 solution for gamified turism, involving users, public administration and local businesses.}
            \item {Demo presented at Laboratorio de Patrimonio Cultural at Las Cinco VIllas (Zaragoza).}
        \end{cvitems}
    }

%---------------------------------------------------------
    \cventry
    {Senior AI Engineer} % Advisor
    {Accenture Technology} % Institution
    {Madrid, Spain} % Location
    {Feb. 2019 - Sep. 2021} % Date(s)
    {
        \begin{cvitems} % Description(s)
            \item {Development of cognitive systems: Virtual assistants, NLP and Image Recognition.}
            \item {Development of a mobile virtual assistant for one of the biggest Spanish electrical companies including: }
                \subitem {Design of custom NLP neural architectures in Tensorflow.}
                \subitem {CI/CD using Jira's suite and agile methodologies in AWS.}
                \subitem {Design of workflows and reporting using Kibana and ElasticSearch.}
                \subitem {Design of conversational flows using RASA.}
                \subitem {Deployment of the whole system in AWS via Kubernetes.}
            \item {Implementation of Salesforce Einstein solutions for CRMs.}
            \item {Leadership of the spanish technical team in the development of a global AI solution for a big Italian energy company.}
        \end{cvitems}
    }

%---------------------------------------------------------
    \cventry
    {Plannification Assistant} % Year
    {Banco Santander} % Position
    {Las Rozas, Spain} % Institution
    {June 2018 - Feb 2019} % Location
    {
        \begin{cvitems} % Description(s)
            \item {Part of the Planning, Productivity and Quality department at Banco Santander, where we mainly make predictions for the working curves for different front and back office services.}
            \item {Development and improvement of company’s reports and digital tools in cooperation with IT department.}
            \item {Collaboration with business, front and back office areas in designing pilot processes for efficiency improvements.}
            \item {Improvement of data acquisition and analysis in collaboration with IT department.}
            \item {Collaboration with business areas in the development of SLAs and KPIs related to the planning, adhesion, and efficiency of the services.}
            \item {Design and acquisition of quality reports using QlikView.}
        \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
