%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publications}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------

%---------------------------------------------------------
\cvsubsection{Published}
%---------------------------------------------------------
\begin{cvpubs}

    \cvpub{Blanco-Fernández E., \textbf{Gutiérrez-Alvarez C.}, Nasri N., Maldonado-Bascón S., López-Sastre R.J., \textit{Live Video Captioning}, in Multimedia Tools and Applications, 2025.}

    \cvpub{\textbf{Gutiérrez-Alvarez C.}, Ríos-Navarro P., Flor-Rodríguez-Rabadán R., Acevedo-Rodríguez F.J., López-Sastre R.J., \textit{Visual Semantic Navigation with Real Robots}, in Applied Intelligence, 2024.}

    \cvpub{\textbf{Gutiérrez-Alvarez C.}, Acevedo-Rodríguez F.J., López-Sastre R.J., Kanezaki A., OffNav: \textit{Offline Reinforcement Learning for Visual Semantic Navigation}, in ICRA Human-aligned Reinforcement Learning for Autonomous Agents and Robots Workshop, 2024.}

    \cvpub{Lafuente-Arroyo S., Maldonado-Bascón S., Delgado-Mena D., \textbf{Gutiérrez-Alvarez C.}, Acevedo-Rodríguez F.J., \textit{Multisensory Integration for Topological Indoor Localization of Mobile Robots in Complex Symmetrical Environments}, in Expert Systems with Applications, 2023.}

    \cvpub{\textbf{Gutiérrez-Alvarez C.}, Ríos-Navarro P., Flor-Rodríguez-Rabadán R., Acevedo-Rodríguez F.J., López-Sastre R.J., \textit{Evaluation of Visual Semantic Navigation Models in Real Robots}, in IROS Late Breaking Results, 2023.}

    \cvpub{\textbf{Gutiérrez-Alvarez C.}, Hernández García S, Nasri N, Cuesta-Infante Alfredo, López-Sastre RJ, \textit{Towards Clear Evaluation of Robotic Visual Semantic Navigation}, in ICARA, 2023.}

    \cvpub{Nasri N, López-Sastre RJ, Pacheco-da-Costa S, Fernández-Munilla I, \textbf{Gutiérrez-Álvarez C.}, Pousada-García T, Acevedo-Rodríguez FJ, Maldonado-Bascón S. \textit{Assistive Robot with an AI-Based Application for the Reinforcement of Activities of Daily Living: Technical Validation with Users Affected by Neurodevelopmental Disorders}, in Applied Sciences, 2022.}

\end{cvpubs}
% %---------------------------------------------------------

%% %---------------------------------------------------------
\cvsubsection{Preprints}

\begin{cvpubs}

    \cvpub{Nasri N., \textbf{Gutiérrez-Álvarez C.}, Lafuente-Arroyo S., Maldonado-Bascón S., López-Sastre R.J. \textit{Realistic Continual Learning Approach using Pre-trained Models,} in ArXiv 2024, abs/2404.07729.}

\end{cvpubs}



% %---------------------------------------------------------
